\begin{fullwidth}
\section{Problem Statement}
    Futuristic Innovative Technologies (FIT) is a high-end producer of specialized UAV systems for extreme applications working to produce a feasibility study for building an Autonomous UAV (AUAV). This new AUAV would integrate state-of-the-art Atmospheric Turbulence Compensation (ATC) imaging capabilities with General Purpose Parallel Processing (GPPP) technology in real time, perform “search and find” maneuvers, track objects-of-interests, and avoid perceived threats. In addition to advanced optics that have ATC capability, the AUAV will have a hyperspectral and polarimetric imaging system on board that will be able to classify target composition from altitude. The AUAV must also be worldwide deployable, minimize or eliminate the use of sensitive electronics components, and have a neutral, nondescript profile.
    
    The AUAV will be controllable from a Mobile Command Center (MCC) that is capable of being powered off-grid for an indefinite amount of time in remote and low-access areas. The power requirements for the MCC are estimated to be 70-80 kWh and must utilize renewable energy resources as much as possible. The cabin of the MCC must also be human comfortable and able to give operators complete access to the AUAV command and control network as well as diagnostic and maintenance information. A component-level, bottom-up analysis of the MCC will also be performed in conjunction with the AUAV study.

\section{Mission Statement}
    The mission of the three-letter agency is to provide multi-purpose surveillance support for worldwide scientific collection activities, support low-profile data and information collection efforts for allies and national partners, conduct rapid worldwide deployments and surveillance activities in support of national treaty monitoring interests, and implement surveillance and reconnaissance missions for national strategic and tactical targets-of-interest (TOIs). The three-letter fosters science, innovative technology, and collaborations with strategic partners. 
    
\end{fullwidth}