\begin{fullwidth}
\section{Scope}
\subsection{scope statement}
The project's goals include integrating cutting-edge imaging capabilities in real time, performing "search and find" maneuvers, object of interest tracking.It is also designed to be extensible for future features and to account for the effects of atmospheric turbulence on imaging distortion and automatic target recognition. Additionally, FIT will conduct a feasibility assessment for the creation of a Mobile Command Center (MCC), which will be able to be permanently deployed in isolated, difficult-to-reach locations. The primary components of this project that must be internalized are:
\begin{itemize}
\item{Automatic Target Recognition (ATR) capability and high-speed atmospheric turbulence compensation(ATC).}

\item{The ability to track objects of interest (OoI) and conduct "search and locate" maneuvers, all autonomously.}

\item{provides advanced material and background discriminating capabilities with a polarimetric and hyperspectral imaging system.}

\item{The capacity to use a flexible system to augment other characteristics or capabilities based on the mission or environment in which it will be deployed.}
\end{itemize}
Features recommended for integration into AUAV must resemble generic 'Search and Rescue' characteristics for global deployment. The project's specific goal is to provide desert, coastline, and Alaskan wilderness search and rescue abilities, with an emphasis on adaptation to detect obstacles and resist itself owing to challenging conditions and circumstances. The system should be able to operate autonomously or be operated remotely.

\subsection{Scope Boundaries}
Below table categorizes the project tasks into 3 parts which are inter-related and integrated technologies.
\begin{table}
\centering
    \begin{tabular}{|p{5cm}| p{7cm}| p{2cm}|}
         \hline
          \rowcolor[gray]{0.8}
         System & Anticipated Task(s) & Exclusions\\[1ex]
         \hline
         Imaging capability with Atmospheric turbulence compensating system& \begin{itemize}
             \item {State-of-art technology}
             \item{Producing High spatial resolution images}
             \item{Environmental conditioning}
         \end{itemize}
         & None\\
        \hline
        Autonomous flight control system &
        \begin{itemize}
            \item{Object of interest tracking}
            \item{"Search and find" maneuvers}
            \item{Controllable manual over-ride}
            \item{Detect and identify target of Interest}
            \item{Controlled by a live operator}
        \end{itemize}
        & None\\
        \hline
        Adaptability&
        \begin{itemize}
            \item {Modular AUAV}
            \item{deploy-able World-wide, anytime of the day}
            \item{should be operable  even in extreme environment}
            \item{ability to be updated with newer hardware parts and software respectively}
            \item{disguised as a "search and rescue" AUAV}
        \end{itemize}
        & None\\
        \hline
    \end{tabular}
\end{table}
\end{fullwidth}